---
title: "Report"
output: pdf_document
fig_caption: yes
fontsize: 12pt
date: "`r format(Sys.time(), '%d %B, %Y')`"
---


```{r functions, echo=FALSE, include=FALSE, message=FALSE , warning=FALSE}
# A function for captioning and referencing images
fig <- local({
    i <- 0
    ref <- list()
    list(
        cap=function(refName, text) {
            i <<- i + 1
            ref[[refName]] <<- i
            paste("Figure ", i, ": ", text, sep="")
        },
        ref=function(refName) {
            ref[[refName]]
        })
})
```

##  Estimation of optimal intensity of observation over	incidence

```{r run, include=FALSE, echo=FALSE, message=FALSE}
n.run
```

```{r time, include=FALSE, echo=FALSE, message=FALSE}
time.t
```

```{r min, include=FALSE, echo=FALSE, message=FALSE}
as.numeric(estim.t[estim.t$estim==min(as.numeric(estim.t$estim)),]$l)
```

For this task there was done `r n.run` model runs with modeling time `r time.t` and current properties (*Table 1*).

```{r kable, message=FALSE, results = 'asis', echo=FALSE, scientific=FALSE}
knitr::kable(cp[,c("Character", "Value")], format.args = list(scientific=T), 
             caption = "Input variable for simulation.")
```

As a result of minimization of functional $\Phi^{(m)}_T(\gamma^{(m)})$ estimation of 
**optimal intensity of observation** is equal to **`r as.numeric(estim.t[estim.t$estim==min(as.numeric(estim.t$estim)),]$l)`** . 
You can see functional values on *Figure 1*.

```{r plot1, message=FALSE, echo=FALSE, fig.cap=paste("Estimation of monitoring intensity. Green line depicts values of functional, and blue line means optimal observation intensity.")}
# plot.col <- c("#999999", "#E69F00", "#56B4E9", "#33a02c")
# number_of_people(abund.log,0,350, save = F, inp.title = "Shigella", col.pal = plot.col)
knitr::include_graphics(paste(out.folder,"/tmp/plot.pdf", sep="") ) 
```
